\LARGE \bf \pyRobots{}, a toolset for robot executive control

### 2014-09-29 root.tex
paper.tex -> root.tex (mandated by ICRA)

Any robotic experiment requires a certain amount of high-level control to
supervise the robot behaviour, and, expectedly, many projects have attempted to
design and provide tools for this task. Degroote provides an in-depth review of
the existing techniques and tools in~\cite{degroote2012architecture}. We focus
this review on tools dedicated to the explicit implementation of high-level
behaviours, excluding complete control stacks (that would typically include a
middleware and hardware abstractions), meta-tools (such as component generators
or model checkers) and (semi-)automatic techniques (such as emerging behaviours
or learning by demonstration). Unlike \emph{middlewares} where a few tools --
ROS, YARP, {\sc orocos}-rtt, OpenRTM -- are the \emph{de facto} standards, no tool really
dominate the field of execution control, and we believe instead that most of
today's robot behaviours are implemented as \emph{ad-hoc} scripts.

>>>>

Any robotic experiment requires a certain amount of high-level control to
supervise the robot behaviour, and, expectedly, many projects have attempted to
design and provide tools for this task. Degroote provides an in-depth review of
the existing techniques and tools in~\cite{degroote2012architecture}. We focus
this review on tools dedicated to the explicit implementation of high-level
behaviours, excluding complete control stacks (that would typically include a
middleware and hardware abstractions), meta-tools (such as component generators
or model checkers) and (semi-)automatic techniques (such as emerging behaviours
or learning by demonstration). Unlike \emph{middlewares} where a few tools --
ROS, YARP, {\sc orocos}-rtt, OpenRTM -- are the \emph{de facto} standards, no tool really
dominates the field of execution control, and we believe instead that most of
today's robot behaviours are implemented as \emph{ad-hoc} scripts.
